Evolution of solar wind discontinuities in the inner heliosphere

### 2024-01-25 index.qmd
update
add notes

---
title: Psp_conjunction
bibliography: files/references.bib
---

## PSP Encounter Infos

@@

| Event | Distance                    | Time                         |
|-------|-----------------------------|------------------------------|
| E1    | 35.6 $R_{\odot}$            | Perihelion: 2018-11-06 03:27 |
| E2    | 35.6 $R_{\odot}$            | Perihelion: 2019-04-04 22:39 |
| E3    | 35.6 $R_{\odot}$            | Perihelion: 2019-09-01 17:50 |
| E4    | 27.8 $R_{\odot}$            | Perihelion: 2020-01-29 09:37 |
| E5    | 27.8 $R_{\odot}$            | Perihelion: 2020-06-07 08:23 |
| E6    | 20.3 $R_{\odot}$            | Perihelion: 2020-09-27 09:16 |
| E7    | 20.3 $R_{\odot}$            | Perihelion: 2021-01-17 17:40 |
| E8    | 0.074 AU (15.9 $R_{\odot}$) | Perihelion: 2021-04-29 08:48 |
| E9    | 15.9 $R_{\odot}$            | Perihelion: 2021-08-09 19:11 |
| E10   | 13.3 $R_{\odot}$            | Perihelion: 2021-11-21 08:23 |
| E11   | 13.3 $R_{\odot}$            | Perihelion: 2022-02-25 15:38 |
| E12   | 13.3 $R_{\odot}$            | Perihelion: 2022-06-01 22:51 |
| E13   | 13.3 $R_{\odot}$            | Perihelion: 2022-09-06 06:04 |
| E14   | 13.3 $R_{\odot}$            | Perihelion: 2022-12-11 13:16 |
| E15   | 13.3 $R_{\odot}$            | Perihelion: 2023-03-17 20:30 |
| E16   | 13.3 $R_{\odot}$            | Perihelion: 2023-06-22 03:46 |
| E17   | 11.4 $R_{\odot}$            | Perihelion: 2023-09-27 23:28 |
| E18   | 11.4 $R_{\odot}$            | Perihelion: 2023-12-29 00:54 |
| E19   | 11.4 $R_{\odot}$            | Perihelion: 2024-03-30 02:20 |
| E20   | 11.4 $R_{\odot}$            | Perihelion: 2024-06-30 03:46 |
| E21   | 11.4 $R_{\odot}$            | Perihelion: 2024-09-30 05:13 |
| E22   | 9.9 $R_{\odot}$             | Perihelion: 2024-12-24 11:41 |
| E23   | 9.9 $R_{\odot}$             | Perihelion: 2025-03-22 22:25 |
| E24   | 9.9 $R_{\odot}$             | Perihelion: 2025-06-19 09:09 |

>>>>

---
title: Evolution of solar wind discontinuities in the inner heliosphere
subtitle: PSP and Earth conjunctions and alignments
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=PZ6j7iriic2l
    text: Tana
  - href: zotero://select/library/collections/L9JC7XAI
    text: Zotero
---

# Updates

![](images/paste-11.png)

![](images/paste-12.png)

# References

- @velliUnderstandingOriginsHeliosphere2020
- @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
    - > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.

# PSP Encounter Infos

@@

{{< embed notebooks/00_notes.ipynb#tbl-events >}}
